---
title: "MacDougal et al. 2025 Soil Physical Properties Analysis"
author: "Elizabeth MacDougal"
date: "2024-2025"
output:
  html_document:
    toc: true
    df_print: paged
  pdf_document:
    latex_engine: xelatex
    toc: true
geometry: margin=1in
editor_options:
  markdown:
    wrap: 72
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir='~/Tulane/1_VBL/2_ReCoast/Paper Growth/Analysis/Publish')
knitr::opts_chunk$set(
  dev = "png",
  dpe = 300,
  echo = FALSE,
  cache = TRUE
)
options(contrasts=c("contr.helmert","contr.poly"));options("contrasts")
```

newpage

# Description

This file accompanies the paper "Wetland plant growth in recycled glass
sand versus dredged river sand: Evaluating a new resource for coastal
restoration." Paper authors: Elizabeth MacDougal, Bek Markel, Emily
Farrer, Shehbaz Ahmad, Julie Albert, Sunshine Van Bael. Analyses in this
file were conducted by Elizabeth MacDougal. Corresponding author:
Elizabeth MacDougal,
[emacdougal\@tulane.edu](mailto:emacdougal@tulane.edu){.email}

Funding was provided by National Science Foundation Convergence
Accelerator Program Award Number 2137730.

SA conducted soil bulk density, porosity, permeability, and compaction
tests, advised by JA.

## Purpose of this File

This file includes all soil physical properties analyses described in
the paper. It serves to provide more detail to those who are curious,
and to help others reproduce the results.

# Environment Setup

Load in the libraries I plan to use:

```{r, warning=FALSE}
library(dplyr)#DATA ORGANIZATION %>% symbol is used for "piping."
library(nlme) #DATA ORGANIZATION. Tidyr is in here, and this lets me rearrange my data. 
library(plotrix) #PLOTTING DATA. For means and standard error, to set error bars on plots. 
library(tidyverse)#PLOTTING DATA. Useful for customizing plots
library(ggpmisc)#PLOTTING DATA. Includes ggplot2 and ggpp.
library(patchwork)#PLOTTING DATA. Plot multiple ggplots together in one figure
library(ggpattern) #PLOTTING DATA. Used to add texture to graphs
library(multcomp) #ANALYZING DATA. Used for glht, for Tukey Tests
library(modelbased) #For calculating marginal means
#library(easystats) # To help with graphing models with ggplot https://easystats.github.io/see/
library(vegan)
library(car) #For testing heterogeneity with Levene's Test
```

# Porosity

## Porosity Data

The column "Substrate" corresponds with soil types in the paper.

| Substrate in Porosity.csv | Corresponding soil type in the paper |
|---------------------------|--------------------------------------|
| Fine                      | Fine glass sand                      |
| CoarseA                   | Broad range coarse glass sand        |
| CoarseB                   | Mid-range coarse glass sand          |
| MixA                      | Broad range glass/dredge mix         |
| MixB                      | Mid-range glass/dredge mix           |
| Dredge                    | Dredge                               |

```{r}
porosity <- read.csv("./Porosity.csv",stringsAsFactors = T)
porosity$Substrate <- factor(porosity$Substrate, levels=c("Fine","CoarseA","CoarseB","MixA","MixB","Dredge"))


porositywet <- read.csv("./Compaction_November.csv")
porositywet$Substrate <- factor(porosity$Substrate, levels=c("Fine","CoarseA","CoarseB","MixA","MixB","Dredge"))
```

## Porosity Models

### Dry Porosity Model

```{r}
dryporositygls <- gls(Porosity ~ Substrate,
                   weights = varIdent(form = ~ 1 | Substrate),
                   method = "REML",
                   data=porosity)

dryporositygls2 <- gls(Porosity ~ Substrate,
                   method = "REML",
                   data=porosity)

anova(dryporositygls,dryporositygls2)

bartlett.test(Porosity ~ Substrate, data = porosity)
leveneTest(Porosity ~ Substrate, data = porosity)
#accounting for variance produces a better model. According to the Levene test, this is not necessary, but according to the bartlett.test (more sensitive) it is. 
#We will go with the Levene test, because this is what we did for Biomass. So porositygls2
```

### Dry Porosity Validation

```{r}
hist(resid(dryporositygls2, type = "normalized"))
#Pretty good
plot(fitted(dryporositygls2),
     resid(dryporositygls2, type = "normalized"))
#Not bad

anova(dryporositygls2, type = "marginal")
summary(dryporositygls2)
```

### Dry Porosity Tukey

```{r, tukey porosity}
tukeydryporosity <- summary((glht(dryporositygls2, linfct = mcp(Substrate=c("CoarseA-Fine=0","CoarseB-Fine=0","MixA-Fine=0","MixB-Fine=0", "Dredge-Fine=0","CoarseB-CoarseA=0","MixA-CoarseA=0","MixB-CoarseA=0", "Dredge-CoarseA=0","MixA-CoarseB=0","MixB-CoarseB=0", "Dredge-CoarseB=0","MixB-MixA=0","Dredge-MixA=0","Dredge-MixB=0")))))

tukeydryporosity
```

### Wet Porosity Model

```{r}
porositygls <- gls(SaturatedCompressedPorosity ~ Substrate,                    
                   weights = varIdent(form = ~ 1 | Substrate),                    method = "REML",                    
                   data=porositywet)  
porositygls2 <- gls(SaturatedCompressedPorosity ~ Substrate,                  
                    method = "REML",                    
                    data=porositywet) 

anova(porositygls,porositygls2)  

bartlett.test(SaturatedCompressedPorosity ~ Substrate, data = porositywet) 

leveneTest(SaturatedCompressedPorosity ~ Substrate, data = porositywet) 
#We should not account for variance: simpler model lower AIC and variance not heterogeneous according to both tests.
```

### Wet Porosity Validation

```{r}

hist(resid(porositygls2, type = "normalized")) #Pretty good but skewed left

plot(fitted(porositygls2),      
     resid(porositygls2, type = "normalized")) 

#Not bad 

anova(porositygls2)
#saturated, compressed porosity is impacted by substrate.
```

### Wet Porosity Tukey

```{r, tukey porosity wet}
tukeyporositywet <- summary((glht(porositygls2, linfct = mcp(Substrate=c("CoarseA-Fine=0","CoarseB-Fine=0","MixA-Fine=0","MixB-Fine=0", "Dredge-Fine=0","CoarseB-CoarseA=0","MixA-CoarseA=0","MixB-CoarseA=0", "Dredge-CoarseA=0","MixA-CoarseB=0","MixB-CoarseB=0", "Dredge-CoarseB=0","MixB-MixA=0","Dredge-MixA=0","Dredge-MixB=0")))))

tukeyporositywet
```

Fine differs from: Coarse B, Mix B, Dredge Coarse A differs from: Coarse
B, Mix B, Dredge Coarse B differs from: Mix A, Mix B Mix A differs from:
Dredge Mix B differs from: Dredge

## Porosity Stats

```{r, mean se porosity}
porositymeanse <-
  porosity %>%
  group_by(Substrate) %>%
  summarise(mean = mean(Porosity),
            se = std.error(Porosity)
            )
porositymeanse$me <- porositymeanse$se*1.96
porositymeanse$min <- porositymeanse$mean-porositymeanse$me
porositymeanse$max <- porositymeanse$mean+porositymeanse$me
porositymeanse

porositywetmeanse <-
  porositywet %>%
  group_by(Substrate) %>%
  summarise(mean = mean(SaturatedCompressedPorosity),
            se = std.error(SaturatedCompressedPorosity)
            )
porositywetmeanse$me <- porositywetmeanse$se*1.96
porositywetmeanse$min <- porositywetmeanse$mean-porositymeanse$me
porositywetmeanse$max <- porositywetmeanse$mean+porositymeanse$me
porositywetmeanse
```

## Porosity Plots

### Dry Porosity Plot

```{r, dryporosityplots}
my_combo_colors <- c("gold","goldenrod2","goldenrod3", "chartreuse3","chartreuse4", "skyblue3")
plotporosity <- ggplot(porosity, aes(Substrate, Porosity)) +
  geom_point(aes(color=Substrate),
    alpha = 0.85,
    position = position_jitter(height = 0, width = 0.2),
    size = 1.5,
    show.legend = FALSE
  ) +
  scale_color_manual(values = my_combo_colors) +
  stat_summary(
    fun.data = mean_se,
    geom = "errorbar",
    width = 0.2,
    colour = "black",
    alpha = 1
  ) +
  stat_summary(
    fun = mean,
    geom = "point",
    fill = "black",
    pch = 21,
    size = 2
  ) +
  theme_bw()

plotporosity

# ggsave(
#   filename = "./Figures/plotporosity_January.pdf",
#   plot = last_plot(),
#   device = NULL,
#   path = NULL,
#   scale = 1,
#   width = 3.5,
#   height = 2.5,
#   units = c("in"),
#   dpi = 600,
#   limitsize = TRUE,
#   bg = NULL,
#   create.dir = FALSE
# )

```

### Wet Porosity Plot

```{r, wetporosityplots}
my_combo_colors <- c("gold","goldenrod2","goldenrod3", "chartreuse3","chartreuse4", "skyblue3")
plotporositywet <- ggplot(porositywet, aes(Substrate, SaturatedCompressedPorosity)) +
  geom_point(aes(color=Substrate),
    alpha = 0.85,
    position = position_jitter(height = 0, width = 0.2),
    size = 1.5,
    show.legend = FALSE
  ) +
  scale_color_manual(values = my_combo_colors) +
  stat_summary(
    fun.data = mean_se,
    geom = "errorbar",
    width = 0.2,
    colour = "black",
    alpha = 1
  ) +
  stat_summary(
    fun = mean,
    geom = "point",
    fill = "black",
    pch = 21,
    size = 2
  ) +
  theme_bw()

plotporositywet

# ggsave(
#   filename = "./Figures/plotwetporosity_January.pdf",
#   plot = last_plot(),
#   device = NULL,
#   path = NULL,
#   scale = 1,
#   width = 3.5,
#   height = 2.5,
#   units = c("in"),
#   dpi = 600,
#   limitsize = TRUE,
#   bg = NULL,
#   create.dir = FALSE
# )
```

# Particle Density

## Particle Density Data

Particle density data is in with the porosity data.

```{r}
porosity <- read.csv("./Porosity.csv",stringsAsFactors = T)
porosity$Substrate <- factor(porosity$Substrate, levels=c("Fine","CoarseA","CoarseB","MixA","MixB","Dredge"))

```

## Particle Density Models

```{r}
pdgls2 <- gls(ParticleDensity_gperml ~ Substrate,
                   weights = varIdent(form = ~ 1 | Substrate),
                   method = "REML",
                   data=porosity)

pdgls <- gls(ParticleDensity_gperml ~ Substrate,
                   method = "REML",
                   data=porosity)

anova(pdgls,pdgls2)
bartlett.test(ParticleDensity_gperml ~ Substrate, data = porosity)
leveneTest(ParticleDensity_gperml ~ Substrate, data = porosity)
# the more complex model has lower AIC, and the data fail the bartlett and levene tests, so we should use pdgls2.
```

## Particle Density Validation

```{r}
hist(resid(pdgls2, type = "normalized"))
#okay
plot(fitted(pdgls2),
     resid(pdgls, type = "normalized"))
#alright

anova(pdgls2)
summary(pdgls2)
```

## Particle Density Tukey

```{r, tukey partdens}
tukeypd <- summary((glht(pdgls2, linfct = mcp(Substrate=c("CoarseA-Fine=0","CoarseB-Fine=0","MixA-Fine=0","MixB-Fine=0", "Dredge-Fine=0","CoarseB-CoarseA=0","MixA-CoarseA=0","MixB-CoarseA=0", "Dredge-CoarseA=0","MixA-CoarseB=0","MixB-CoarseB=0", "Dredge-CoarseB=0","MixB-MixA=0","Dredge-MixA=0","Dredge-MixB=0")))))

tukeypd
```

## Particle Density Stats

```{r, mean se particle density}
pdmeanse <-
  porosity %>%
  group_by(Substrate) %>%
  summarise(mean = mean(ParticleDensity_gperml),
            se = std.error(ParticleDensity_gperml)
            )
pdmeanse$me <- pdmeanse$se*1.96
pdmeanse$min <- pdmeanse$mean-pdmeanse$me
pdmeanse$max <- pdmeanse$mean+pdmeanse$me
pdmeanse
```

## Particle Density Plots

```{r, porosityplots}
my_combo_colors <- c("gold","goldenrod2","goldenrod3", "chartreuse3","chartreuse4", "skyblue3")
plotpd <- ggplot(porosity, aes(Substrate, ParticleDensity_gperml)) +
  geom_point(aes(color=Substrate),
    alpha = 0.65,
    position = position_jitter(height = 0, width = 0.2),
    size = 1.5,
    show.legend = FALSE
  ) +
  scale_color_manual(values = my_combo_colors) +
  stat_summary(
    fun.data = mean_se,
    geom = "errorbar",
    width = 0.2,
    colour = "black",
    alpha = 1
  ) +
  stat_summary(
    fun = mean,
    geom = "point",
    fill = "black",
    pch = 21,
    size = 2
  ) +
  theme_bw()

plotpd

# ggsave(
#   filename = "./Figures/plotpd_January.pdf",
#   plot = last_plot(),
#   device = NULL,
#   path = NULL,
#   scale = 1,
#   width = 3.5,
#   height = 2.5,
#   units = c("in"),
#   dpi = 600,
#   limitsize = TRUE,
#   bg = NULL,
#   create.dir = FALSE
# )
```

# Bulk Density

## BD Data

SoilType column in DryBulkDensity.csv corresponds with soil types in the
paper.

| SoilType in DryBulkDensity.csv | Corresponding soil type in the paper |
|--------------------------------|--------------------------------------|
| Fine                           | Fine glass sand                      |
| CoarseA                        | Broad range coarse glass sand        |
| CoarseB                        | Mid-range coarse glass sand          |
| MixA                           | Broad range glass/dredge mix         |
| MixB                           | Mid-range glass/dredge mix           |
| Dredge                         | Dredge                               |

```{r}
bulkdens <- read.csv("./DryBulkDensity.csv",stringsAsFactors = T) %>% group_by(SoilType)


bulkdens$SoilType <- factor(bulkdens$SoilType, levels = c("Fine","CoarseA","CoarseB","MixA","MixB","Dredge"))

compaction <- read.csv("./Compaction_November.csv") %>% group_by(SoilType)

compaction$SoilType <- factor(compaction$SoilType, levels = c("Fine","CoarseA","CoarseB","MixA","MixB","Dredge"))

```

## BD Models

### Dry Uncompressed Model

```{r}
bddrygls <- gls(BDUncompressed_gperml_Rounded ~ SoilType, 
                  weights = varIdent(form = ~ 1 | SoilType),
                  method = "REML", 
                  data = bulkdens)
bddrygls2 <- gls(BDUncompressed_gperml_Rounded ~ SoilType, 
                  method = "REML", 
                  data = bulkdens)

anova(bddrygls,bddrygls2)

bartlett.test(BDUncompressed_gperml_Rounded ~ SoilType, data = bulkdens)
#Variances are homogeneous and it's lower AIC not to include them in the model.
leveneTest(BDUncompressed_gperml_Rounded ~ SoilType, data = bulkdens)
```

### Dry Uncompressed Validation

```{r}
hist(resid(bddrygls2, type = "normalized"))
#Pretty good
plot(fitted(bddrygls2),
     resid(bddrygls2, type = "normalized"))
#Pretty good
anova(bddrygls)
```

### Dry Uncompressed Tukey

```{r, tukey bddry}
tukeybddry <- summary(glht(bddrygls2,linfct = mcp(SoilType=c("CoarseA-Fine=0","CoarseB-Fine=0","MixA-Fine=0","MixB-Fine=0", "Dredge-Fine=0","CoarseB-CoarseA=0","MixA-CoarseA=0","MixB-CoarseA=0", "Dredge-CoarseA=0","MixA-CoarseB=0","MixB-CoarseB=0", "Dredge-CoarseB=0","MixB-MixA=0","Dredge-MixA=0","Dredge-MixB=0"))))
tukeybddry
```

### Dry Unompressed Stats

```{r, meanse bd dry}
drybdmeanse <-
  bulkdens %>%
  group_by(SoilType) %>%
  summarise(mean = mean(BDUncompressed_gperml_Rounded),
            se = std.error(BDUncompressed_gperml_Rounded)
            )
drybdmeanse$me <- drybdmeanse$se*1.96
drybdmeanse$min <- drybdmeanse$mean-drybdmeanse$me
drybdmeanse$max <- drybdmeanse$mean+drybdmeanse$me
drybdmeanse
```

### Saturated Compressed Model

This model is based on data estimated from average dry bulk density. It
assumes that the uncompressed saturated and unsaturated bulk densities
are equivalent. However, Saturated bulk densities are likely more
compressed, according to SA.

```{r}
bdsatcompestgls2 <- gls(BD_SaturatedCompressed_Estimated_gperml ~ SoilType, 
                  weights = varIdent(form = ~ 1 | SoilType),
                  method = "REML", 
                  data = compaction)
bdsatcompestgls <- gls(BD_SaturatedCompressed_Estimated_gperml ~ SoilType, 
                  method = "REML", 
                  data = compaction)
anova(bdsatcompestgls,bdsatcompestgls2)

bartlett.test(BD_SaturatedCompressed_Estimated_gperml ~ SoilType, data = compaction)
#Variances are homogeneous and it's lower AIC not to include them in the model.
leveneTest(BD_SaturatedCompressed_Estimated_gperml ~ SoilType, data = compaction)
```

### Saturated Compressed Validation

```{r}
hist(resid(bdsatcompestgls, type = "normalized"))
#Not great but not terrible
plot(fitted(bdsatcompestgls),
     resid(bdsatcompestgls, type = "normalized"))
#not the best

anova(bdsatcompestgls)
```

### Saturated Compressed Tukey

```{r, tukey bdsatcomp better}

tukeybdsatcompest <- summary(glht(bdsatcompestgls,linfct = mcp(SoilType=c("CoarseA-Fine=0","CoarseB-Fine=0","MixA-Fine=0","MixB-Fine=0", "Dredge-Fine=0","CoarseB-CoarseA=0","MixA-CoarseA=0","MixB-CoarseA=0", "Dredge-CoarseA=0","MixA-CoarseB=0","MixB-CoarseB=0", "Dredge-CoarseB=0","MixB-MixA=0","Dredge-MixA=0","Dredge-MixB=0"))))
tukeybdsatcompest

```

### Saturated Compressed Stats

```{r, meanse bd satcomp}
bdmeanse <-
  compaction %>%
  group_by(SoilType) %>%
  summarise(mean = mean(BD_SaturatedCompressed_Estimated_gperml),
            se = std.error(BD_SaturatedCompressed_Estimated_gperml)
            )
bdmeanse$me <- bdmeanse$se*1.96
bdmeanse$min <- bdmeanse$mean-bdmeanse$me
bdmeanse$max <- bdmeanse$mean+bdmeanse$me
bdmeanse
```

All differ except CoarseB and Fine (surprisingly), CoarseA and the Mixes
(expectedly), CoarseA and Dredge, The mixes with themselves, and Dredge
and Mixes.

## BD Plots

### Dry Uncompressed Plot

```{r, plot bd}
my_combo_colors <- c("gold","goldenrod2","goldenrod3", "chartreuse3","chartreuse4", "skyblue3")
  
plotbddry <- ggplot(bulkdens, aes(SoilType, BDUncompressed_gperml_Rounded)) +
  geom_point(aes(color=SoilType),
    alpha = 0.65,
    position = position_jitter(height = 0, width = 0.2),
    size = 1.5,
    show.legend = FALSE
  ) +
  scale_color_manual(values = my_combo_colors) +
  stat_summary(
    fun.data = mean_se,
    geom = "errorbar",
    width = 0.2,
    colour = "black",
    alpha = 1
  ) +
  stat_summary(
    fun = mean,
    geom = "point",
    fill = "black",
    pch = 21,
    size = 2
  ) +
  theme_bw()

plotbddry

ggsave(
  filename = "./Figures/plotbddry_January.pdf",
  plot = last_plot(),
  device = NULL,
  path = NULL,
  scale = 1,
  width = 3.5,
  height = 2.5,
  units = c("in"),
  dpi = 600,
  limitsize = TRUE,
  bg = NULL,
  create.dir = FALSE
)
```

### Saturated Compressed Plot

Dry weight calculated based on average bulk density.

```{r}
plotbdsatcomp <- ggplot(compaction, aes(SoilType, BD_SaturatedCompressed_Estimated_gperml)) +
  geom_point(aes(color=SoilType),
    alpha = 0.65,
    position = position_jitter(height = 0, width = 0.2),
    size = 1.5,
    show.legend = FALSE
  ) +
  scale_color_manual(values = my_combo_colors) +
  stat_summary(
    fun.data = mean_se,
    geom = "errorbar",
    width = 0.2,
    colour = "black",
    alpha = 1
  ) +
  stat_summary(
    fun = mean,
    geom = "point",
    fill = "black",
    pch = 21,
    size = 2
  ) +
  theme_bw()

plotbdsatcomp

# ggsave(
#   filename = "./Figures/plotbdsatcomp_January.pdf",
#   plot = last_plot(),
#   device = NULL,
#   path = NULL,
#   scale = 1,
#   width = 3.5,
#   height = 2.5,
#   units = c("in"),
#   dpi = 600,
#   limitsize = TRUE,
#   bg = NULL,
#   create.dir = FALSE
# )
```

## BD Stats

```{r}
bddrymn1 <- bulkdens %>% group_by(SoilType) %>% summarise(mean = mean(BDUncompressed_gperml_Rounded), se = std.error(BDUncompressed_gperml_Rounded))
bddrymn1

bdsatcompmn1 <- compaction %>% group_by(SoilType) %>% summarise(mean = mean(BD_SaturatedCompressed_Estimated_gperml), se = std.error(BD_SaturatedCompressed_Estimated_gperml))
bdsatcompmn1

bddrymeanse <- bulkdens %>%
  summarise(mean = mean(BDUncompressed_gperml_Rounded),
            se = std.error(BDUncompressed_gperml_Rounded))
bddrymeanse$me <- bddrymeanse$se*1.96
bddrymeanse$min <- bddrymeanse$mean-bddrymeanse$me
bddrymeanse$max <- bddrymeanse$mean+bddrymeanse$me
bddrymeanse

bdsatcompmeanse <- compaction %>%
  summarise(mean = mean(BD_SaturatedCompressed_Estimated_gperml),
            se = std.error(BD_SaturatedCompressed_Estimated_gperml))
bdsatcompmeanse$me <- bdsatcompmeanse$se*1.96
bdsatcompmeanse$min <- bdsatcompmeanse$mean-bdsatcompmeanse$me
bdsatcompmeanse$max <- bdsatcompmeanse$mean+bdsatcompmeanse$me
bdsatcompmeanse
```

# Compaction

## Compaction Data

| SoilType in Compaction.csv | Corresponding soil type in the paper |
|----------------------------|--------------------------------------|
| Fine                       | Fine                                 |
| CoarseA                    | Coarse 1                             |
| CoarseB                    | Coarse 2                             |
| MixA                       | Mix 1                                |
| MixB                       | Mix 2                                |
| Dredge                     | Dredge                               |

```{r}
compaction <- read.csv("./Compaction_November.csv",stringsAsFactors = T) %>% group_by(SoilType)

compaction$SoilType <- factor(compaction$SoilType, levels = c("Fine","CoarseA","CoarseB","MixA","MixB","Dredge"))
```

## Compaction Modeling

```{r}
compactgls2 <- gls(Compaction ~ SoilType, 
                  weights = varIdent(form = ~ 1 | SoilType),
                  method = "REML", 
                  data = compaction)
compactgls <- gls(Compaction ~ SoilType, 
                  method = "REML", 
                  data = compaction)

anova(compactgls,compactgls2)

bartlett.test(Compaction ~ SoilType, data = compaction)
leveneTest(Compaction ~ SoilType, data = compaction)

#This passes both tests of variance, and the simpler model also has a lower AIC.
```

## Compaction Validation

```{r}
hist(resid(compactgls, type = "normalized"))
#not terrible, but skewed right
plot(fitted(compactgls),
     resid(compactgls, type = "normalized"))
#pretty good
anova(compactgls)
```

## Compaction Tukey

```{r}
tukeycompact <- summary(glht(compactgls,linfct = mcp(SoilType=c("CoarseA-Fine=0","CoarseB-Fine=0","MixA-Fine=0","MixB-Fine=0", "Dredge-Fine=0","CoarseB-CoarseA=0","MixA-CoarseA=0","MixB-CoarseA=0", "Dredge-CoarseA=0","MixA-CoarseB=0","MixB-CoarseB=0", "Dredge-CoarseB=0","MixB-MixA=0","Dredge-MixA=0","Dredge-MixB=0"))))
tukeycompact
```

MixB and CoarseA differ. All else equal.

## Compaction Plots

```{r, compactionplots}
my_combo_colors <- c("gold","goldenrod2","goldenrod3", "chartreuse3","chartreuse4", "skyblue3")
plotcompact <- ggplot(compaction, aes(SoilType, Compaction)) +
  geom_point(aes(color=SoilType),
    alpha = 0.65,
    position = position_jitter(height = 0, width = 0.2),
    size = 1.5,
    show.legend = FALSE
  ) +
  scale_color_manual(values = my_combo_colors) +
  stat_summary(
    fun.data = mean_se,
    geom = "errorbar",
    width = 0.2,
    colour = "black",
    alpha = 1
  ) +
  stat_summary(
    fun = mean,
    geom = "point",
    fill = "black",
    pch = 21,
    size = 2
  ) +
  theme_bw()

plotcompact

# ggsave(
#   filename = "./Figures/plotcompact_January.pdf",
#   plot = last_plot(),
#   device = NULL,
#   path = NULL,
#   scale = 1,
#   width = 3.5,
#   height = 2.5,
#   units = c("in"),
#   dpi = 600,
#   limitsize = TRUE,
#   bg = NULL,
#   create.dir = FALSE
# )
```

## Compaction Stats

```{r, mean se Shehbaz}
compactmeanse <-
  compaction %>%
  summarise(mean = mean(Compaction),
            se = std.error(Compaction))
compactmeanse$me <- compactmeanse$se*1.96
compactmeanse$min <- compactmeanse$mean-compactmeanse$me
compactmeanse$max <- compactmeanse$mean+compactmeanse$me
compactmeanse
```
